PCA

### 2019-10-18 analysis/11_pcalda.Rmd
updated tsne and pca plots

```{r setup, include=FALSE}
library(tidyverse)
library(ggfortify)
library(factoextra)
library(cowplot)
library(Rtsne)
library(viridis)
knitr::opts_chunk$set(echo = TRUE, fig.path = '../figures/pca/')

```

@@

a <- ggplot(mypcadf, aes(x = PC1, y = PC2, 
                         color = colData$treatment, 
                         shape = colData$tissue)) +
  geom_point() + labs(x = "PC1: 35.9%", y = "PC2: 32.5%") + theme_minimal(base_size = 6)  +
  theme(legend.title = element_blank(), legend.position = "left")
a

@@

# prep for adding columns
colData$V1 <- NULL
tsne_df_cols <- cbind(colData, tsne_df)

@@

d <- ggplot(tsne_df_cols, aes(x = V1, y = V2, shape = sex, color = treatment)) +
  geom_point(size = 2) +
  theme_minimal(base_size = 6) +
  theme(legend.position = "top") +
  labs(x = "tSNE 1", y = "tSNE 2")

@@

plot_grid(a + theme(legend.position = "none"),
          b + theme(axis.text = element_blank()) + ggtitle(NULL), 
          c + theme(legend.position = "none"),
          d + theme(legend.position = "none"))
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(ggfortify)
library(factoextra)
library(cowplot)
library(Rtsne)
library(viridis)
knitr::opts_chunk$set(echo = TRUE, fig.path = '../figures/pca/')
```

@@

a <- ggplot(mypcadf, aes(x = PC1, y = PC2, 
                         color = colData$treatment, 
                         shape = colData$tissue,
                         alpha = colData$sex)) +
  geom_point(size = 2)  + theme_minimal(base_size = 6)  +
  theme(legend.title = element_blank(), legend.position = "left") +
  scale_alpha_manual(values = c(0.75,1))
a

@@

# prep for adding columns
colData2 <- colData 
colData2$V1 <- NULL
tsne_df_cols <- cbind(colData2, tsne_df)

@@

d <- ggplot(tsne_df_cols, aes(x = V1, y = V2, shape = tissue, color = treatment, alpha = sex)) +
  geom_point(size = 2) +
  theme_minimal(base_size = 6) +
  theme(legend.position = "top") +
  labs(x = "tSNE 1", y = "tSNE 2") +
  scale_alpha_manual(values = c(0.75,1))

@@

plot_grid(a + theme(legend.position = "none"),
          b + theme(axis.text = element_blank()) + ggtitle(NULL), 
          c + theme(legend.position = "none"),
          d + theme(legend.position = "none"))

mylegend <- get_legend(d + theme(legend.position = "bottom"))

ad <- plot_grid(a + theme(legend.position = "none"),d + theme(legend.position = "none"))

plot_grid(ad, mylegend, nrow = 2, rel_heights = c(1,0.1))
```
